---
title: "markdown1"
author: "Orpaz Goldstein"
date: "April 7, 2016"
output: html_document
---

# Ex2_a

## San Francisco Crime Classification
### [Downloaded from a Kaggle competition.](https://www.kaggle.com/c/sf-crime/data?test.csv.zip)
#### The idea of this competition is to predict the category of crimes commited in San Fransisco. But for this drill i will start with analyzing the most dangerous area and time for a crime to happen, and use these results for the competition.

```{r}
# install.packages("RCurl")
#library(RCurl)

#URL <- "https://www.kaggle.com/c/sf-crime/download/test.csv.zip"
#x <- getURL(URL)
## Or 
#x <- getURL(URL, ssl.verifypeer = FALSE)
#data <- read.csv(text = x)

#if Already downloaded
data <- read.csv("/Users/orpaz/Downloads/test.csv", header=T, sep=",")


head(data)
```

###### The data set contains an id, time stamp, day of week, district in SF, address, geolocation.  I filtered and added an 'hour' collumn so i can more effectively filter the time of the crime.

```{r}
library(lubridate)
data$hour <- c(hour(data$Dates))
```

###### The data set contains an id, time stamp, day of week, district in SF, address, geolocation.  I filtered and added an 'hour' collumn so i can more effectively filter the time of the crime.


* First i checked what day of the week crime accures. <br>

```{r}
barplot(table(data$DayOfWeek), col='blue')
```

  Seemed that they crime accures about the same on every day. <br>

* Next i checked if a certain area has higher crime rate then others. <br>

```{r}
barplot(table(data$PdDistrict), col='blue')
```

  Looks like Southern leads the crime rate in SF! <br>

* Now i want to see what at what time criminals like working <br>

```{r}
barplot(table(data$hour), col='purple')
```

 Crime peaks after-noon from 16-19, also at 12 and midnight...

* Since 18 looks like the most dangerous hour to be outside, i checked what the crime looks like at 18 on the south side of San fransisco <br>
-# getting the map

```{r}
#display results on a map
library(ggmap)

# Subset for South Side
data1 <- subset(data, PdDistrict == 'SOUTHERN')

# Get The Map
map <- get_map(location = c(lon = mean(data1$X), lat = mean(data1$Y)), zoom = 15,
               maptype = "satellite", scale = 2)
# plotting the map with some points on it
ggmap(map) +
  geom_point(data = data1, aes(x = X, y = Y, colour = ifelse(hour==18,F,T), alpha = 0.1), size = 2, shape = 21) +  guides(fill=FALSE, alpha=FALSE, size=FALSE)
```

